---
title: "Mushroom Data Analysis"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

# Index   
1. [Introduction](#introduction) \
2. [Load libraries](#libraries) \
3. [Load data](#data) \
\pagebreak

# Introduction<a name="introduction"></a>

The data set is from the Kaggle website. The data set is about the edible and poisonous mushrooms. The data set has 8124 observations and 24 variables. The variables are as follows:


**1. class:** edible=e, poisonous=p \
**2. cap-diameter:** continuous \
**3. cap-shape:** bell=b, conical=c, convex=x, flat=f, knobbed=k, sunken=s \
**4. cap-surface:** fibrous=f, grooves=g, scaly=y, smooth=s \
**5. cap-color:** brown=n, buff=b, cinnamon=c, gray=g, green=r, pink=p, purple=u, red=e, white=w, yellow=y \
**6. bruises:** bruises=t, no=f \
**7. odor:** almond=a, anise=l, creosote=c, fishy=y, foul=f, musty=m, none=n, pungent=p, spicy=s \
**8. gill-attachment:** attached=a, descending=d, free=f, notched=n \
**9. gill-spacing:** close=c, crowded=w, distant=d \
**10. gill-size:** broad=b, narrow=n \
**11. gill-color:** black=k, brown=n, buff=b, chocolate=h, gray=g, green=r, orange=o, pink=p, purple=u, red=e, white=w, yellow=y \
**12. stalk-shape:** enlarging=e, tapering=t \
**13. stalk-root:** bulbous=b, club=c, cup=u, equal=e, rhizomorphs=z, rooted=r, missing=? \
**14. stalk-surface-above-ring:** fibrous=f, scaly=y, silky=k, smooth=s \
**15. stalk-surface-below-ring:** fibrous=f, scaly=y, silky=k, smooth=s \
**16. stalk-color-above-ring:** brown=n, buff=b, cinnamon=c, gray=g, orange=o, pink=p, red=e, white=w, yellow=y \
**17. stalk-color-below-ring:** brown=n, buff=b, cinnamon=c, gray=g, orange=o, pink=p, red=e, white=w, yellow=y \
**18. veil-type:** partial=p, universal=u \
**19. veil-color:** brown=n, orange=o, white=w, yellow=y \
**20. ring-number:** none=n, one=o, two=t \
**21. ring-type:** cobwebby=c, evanescent=e, flaring=f, large=l, none=n, pendant=p, sheathing=s, zone=z \
**22. spore-print-color:** black=k, brown=n, buff=b, chocolate=h, green=r, orange=o, purple=u, white=w, yellow=y \
**23. population:** abundant=a, clustered=c, numerous=n, scattered=s, several=v, solitary=y \
**24. habitat:** grasses=g, leaves=l, meadows=m, paths=p, urban=u, waste=w, woods=d \

# Load libraries<a name="libraries"></a>

```{r}
library(caret)
library(tidyverse)
```

# Load data<a name="data"></a>

```{r}
mushroom <- read.csv("data/data.csv", sep = ";")
```
